\section{GAME SETUP}

\textit{Campaign Game:} Refer to the back of the battle board card
for game setup.

All army units deploy at full strength and fortresses at their stated strength. Units are placed upright facing their owner’s side of the board. All areas of the map are in play except the French and Russian start areas, which Prussia may never enter, and Sweden until it is at war.

The fortress at Thorn, the Saxon unit and fortress at Dresden, and the Bavarian units are in play.

France, Russia, and Sweden enter the war on Turn 3 of 1757 using the forces noted on the deployment card. Note that the Austrian cavalry Brettlach deploys with the French when they enter the war. Players may want to set these forces up in their start areas during game setup to speed up play.

\textit{Desperate Times Scenario:} This shorter scenario begins in the 4th round of 1757. Players begin with four cards and the VP track is set at three for Prussia holding Dresden.

\textit{Free Deployment}: If players want to try different starting strategies in the Campaign Game, they can use free deployment with these restrictions.

\begin{itemize}
  \setlength\itemsep{-0.5em}
  \item Max one leader per city, units with leader cannot exceed command limit.
  \item Each Prussian fortress must have at least one army unit.
  \item Austria must deploy at least two infantry units in each fortress.
  \item French/Imperial and Russian/Swedish entry are unaffected.
  \item Saxony starts as per the standard Campaign setup.
  \item Fortresses start unaffected.
\end{itemize}